Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-25 Reply_Referee2.tex

\item \textit{``Use $\mathbb{P}$ instead of Pr.''}

Thanks for suggesting a notation choice that could make the exposition easier for readers. We changed it on the latest draft.

\item \textit{``In Algorithm 1, use $\Delta(h,b)$ or $\hat{\Delta}(h,b)$ instead of $\Delta^{*}(h,b)$, as there is no bootstrap uncertainty in the estimated bias. Accordingly in Algorithm 2, use $\Delta^{*}(h,b)$ or $\hat{\Delta}^{*}(h,b)$ instead of $\Delta^{**}(h,b)$.''}

\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{-}$ and $\hat{g}_{+}$''.''}

@@

 Thank you pointing this typo. It has been corrected.

\item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}
%Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.

\item \textit{``In Algorithm 1.2(b) and Algorithm 2.2(b), it should be $X_{i}$ rather than $X^{*}_{i}$.''}

@@

\item \textit{``It will be helpful to have simulation results for DGPs with heteroskedastic variance.''}

 Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.

\item \textit{``In the Mathematical Appendix, the authors used min(h, b), which is redundant. (Page 19, line 4-5)''}

Please see the discussion to about the relationship between $h$ and $b$ in previous comments number 4.

### 2016-07-25 main_paper.tex
Update the basic text for sections 2 and 3 replacing references from residual to wild bootstrap and some other minor changes. NOTE THAT I DID NOT CHANGE THE ALGORITHMS YET. THE LATEST VERSION OF THE ALGORITHMS STILL IS THE ONE AT THE BOOT_RD_GENERAL REPOSITORY. COPY AND PASTE THAT WHEN WE SETTLE ON THE NOTATION AND USE OF I_{h} and I_{b}.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
and higher order derivatives cases (e.g., Regression Kink Designs).

@@

Assumption~\ref{A3} specifies the properties of the kernel function assumed by CCT, which we will also use in this paper.
\begin{assumption}[Kernel]\label{A3}
  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
\end{assumption}

This allows for the vast majority kernel functions commonly used by practitioners. Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model. For simplicity, in the following discussion we use the same function for all steps of estimation.
Potentially different kernel functions could be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.

@@

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a residual bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.
The intuition behind both procedures is straightforward. CCT show that a
local second order polynomial captures the aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
residual bootstrap.

@@

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

Since the second order polynomial captures the relevant aspects of the DGP for
estimating the variance as well as the bias, the asymptotic distribution of the
bias corrected estimator $\hat\tau(h) - \Delta^*(h,b)$ can also be approximated
with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
the same residual bootstrap method used in
Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
and Theorem~\ref{T2} establishes its theoretical properties.

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

>>>>

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD.

@@

Assumption~\ref{A3} specifies the properties of the kernel functions, which are usually assumed by in the literature (see CCT).
\begin{assumption}[Kernel]\label{A3}
  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
\end{assumption}

This allows for the vast majority kernel functions commonly used by practitioners. Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model. For simplicity, in the following discussion we use the same function for all steps of estimation.
Potentially different kernel functions could also be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.

@@

This section presents our theoretical contributions. We propose two algorithms
in this section. The first uses a wild bootstrap based on a second
order local polynomial to estimate the bias of the local linear model. That
estimate can be subtracted from the biased original estimator to provide an
asymptotically unbiased estimator with the same asymptotic distribution as
CCT's. As in CCT, this bias correction term introduces a new source of variance,
invalidating standard (naive) critical values. Consequently, the second
algorithm we propose uses an iterated bootstrap to estimate the correct
critical values of the bias corrected estimator.
The intuition behind both procedures is straightforward. CCT show that a
local second order polynomial captures the aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through a
wild bootstrap.

@@

Under Assumptions~\ref{A1} through ~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} through ~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

Since the second order polynomial captures the relevant aspects of the DGP for
estimating the variance as well as the bias, the asymptotic distribution of the
bias corrected estimator $\hat\tau(h) - \Delta^*(h,b)$ can also be approximated
with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
the same wild bootstrap method used in Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
and Theorem~\ref{T2} establishes its theoretical properties.

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} through ~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}
